Throughput Prediction on 60 GHz Devices for Latency Sensitive Applications

### 2021-01-21 paper.tex
changes

At the MAC layer, the main difference between the IEEE 802.11ad standard compared to the standards governing legacy WiFi is the use of directional communication. Directional communication is required due to the much higher attenuation at the 60 GHz frequency band. To enable directional communication, 802.11ad devices (both APs and clients) perform Sector Level Sweeps (SLS) to train their transmit sectors. During a SLS, each device transmits a Sector Sweep (SSW) control message on each of its transmit sectors, while the other device listens omnidirectionally. Once both sides have transmitted the SSW message on all their transmit sectors, they exchange feedback messages messages indicating to the other side which of their transmit sectors resulted in the highest SNR. The standard does not define the periodicity of the SLS. COTS devices typically perform a SLS every few seconds. In addition, a SLS is triggered during data transmission in case of a missing Block ACK after the number of MAC retries is exceeded.

>>>>

At the MAC layer, the main difference between the IEEE 802.11ad
standard compared to the standards governing legacy WiFi is the use of
directional communication. Directional communication is required due
to the much higher attenuation at the 60 GHz frequency band. To enable
directional communication, 802.11ad devices (both APs and clients)
perform Sector Level Sweeps (SLS) to train their transmit
sectors. During an SLS, each device transmits a Sector Sweep (SSW)
control message on each of its transmit sectors, while the other
device listens omnidirectionally. Once both sides have transmitted the
SSW message on all their transmit sectors, they exchange feedback
messages indicating to the other side which of their transmit sectors
resulted in the highest SNR. The standard does not define the
periodicity of the SLS. COTS devices typically perform an SLS every few
seconds. In addition, an SLS is triggered during data transmission in
case of a missing Block ACK after the number of MAC retries is
exceeded.
